\thesistitle

### 2019-07-22 sections/experimentalsetup.tex
Unrelated

\begin{enumerate}
\item \textbf{Same Interface}: All instances of the clone class are in a class or interface that have a common interface anywhere in their inheritance hierarchy.
\item \textbf{No Direct Superclass}: All instances of the clone class are in a class that does not have any superclass.
\item \textbf{No Indirect Superclass}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
\end{enumerate}

@@

We separate these relations into the following categories, because of their related refactoring opportunities:
\begin{itemize}
  \item \textbf{Common Class}: \textit{Same Method}, \textit{Same Class}
  \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Sibling Class}, \textit{Ancestor Class}, \textit{First Cousin}, \textit{Same Hierarchy}
  \item \textbf{Common Interface}: \textit{Same Interface}
  \item \textbf{Effectively Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{Unrelated}
\end{itemize}

@@

\subsubsection{Effectively Unrelated}
\todo{TODO}

>>>>

\begin{enumerate}
\item \textbf{Same Interface}: All instances of the clone class are in a class or interface that have a common interface anywhere in their inheritance hierarchy.
\item \textbf{No Direct Superclass}: All instances of the clone class are in a class that does not have any superclass.
\item \textbf{No Indirect Superclass}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
\item \textbf{External Ancestor}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
\end{enumerate}

@@

We separate these relations into the following categories, because of their related refactoring opportunities:
\begin{itemize}
  \item \textbf{Common Class}: \textit{Same Method}, \textit{Same Class}
  \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Sibling Class}, \textit{Ancestor Class}, \textit{First Cousin}, \textit{Same Hierarchy}
  \item \textbf{Common Interface}: \textit{Same Interface}
  \item \textbf{Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{External Ancestor}
\end{itemize}

@@

\subsubsection{Unrelated}
Clones are unrelated if they share no common class or interface in their inheritance structure. These clones are least favorable when looking at refactoring, because their refactoring will almost always have a major impact on system design. We formulated four catagories of unrelated clones to look into their refactoring opportunities.

Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent. This marks the opportunity for creating a superclass abstraction and placing the extracted method there. Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors does not have a parent. In such a case, it would be possible to create such an abstraction for the ancestor that does not have a parent.

Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent. Cloned nodes are flagged \textit{External Ancestor} if one of their ancestors has an external parent. Both of these relations obstruct the possibility of creating a superclass abstraction. In such a case, an interface abstraction could be created to make their relation explicit.
